environmental_data_preperation

### 2018-09-11 src/environmental_data_preperation.Rmd
Michael Sumner is a legend!

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
Th
```{r pre-install packages, message=FALSE}
packages <- c("RNetCDF", "raster", "rgdal")
source("./src/ipak.R")
ipak(packages)
suppressMessages(ipak)
```

@@

>>>>

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
Th
```{r pre-install packages, message=FALSE}
packages <- c("RNetCDF", "raster", "rgdal")
source("../src/ipak.R")
ipak(packages)
suppressMessages(ipak)
```

@@

# michael code
```{r}
## use ncdf4 directly
library(ncdf4)
## connection to the file
nc <- nc_open("../data/env/CMEMS_GLOBAL_REANALYSIS_PHY_001_025_salinity_monthly_mean_1993-01.nclonlat.ncdepthtrim.nc")
## desired variable 
v <- ncvar_get(nc, "salinity")
## dimension coordinates
lon <- ncvar_get(nc, "longitude")
lat <- ncvar_get(nc, "latitude")
## a template, one map from the lon, lat, and v[,,1]
template <- raster(list(x = lon, y = lat, z = v[,,1]), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 ")

## apply template to brick, and set values to v (but flipped in Y because that's how raster works - lat is increasing in the NetCDF, so we go upside down)
diy <- setValues(brick(template), v[, ncol(v):1, ])

## target
prj <- "+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
target <- projectExtent(diy, prj)  ## get a target extent, and we'll set the exact resolution we want
res(target) <- c(25000, 25000)
aea <- projectRaster(diy, target)
writeRaster(aea,'../data/env/aea.tif',options=c('TFW=YES'))
plot(aea[[36]]) #the number in brackets refers to the depth number

m <- spTransform(rnaturalearth::ne_countries(), prj)
```
